### 2016-05-31 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Corrected dimension of PPV fan in gas burner report

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

@@

Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure. During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.

>>>>

Tests~2--4 followed an identical order of events. Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test. A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4. During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners. So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame. For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test. To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.

@@

Tests~22 and 23 followed an identical procedure to change the ventilation. Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23. Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25. A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure. During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
